Trends of downward SDR in Thessaloniki 

### 2023-02-13 Article.Rmd
Commit 2023-02-13 20:17

---
title:         "Trends of SDR in Thessaloniki "
author:
  - Natsis Athanasios^[Laboratory of Atmospheric Physics,AUTH, natsisthanasis@gmail.com]
  - Jane Doe^[Institution Two, jane@example.org]
abstract:
  "Study of GHI and DNI radiation for 'clear sky' and all sly conditions."

@@

basic consepts

>>>>

---
title:         "Trends of downward SDR in Thessaloniki "
author:
  - Natsis Athanasios^[Laboratory of Atmospheric Physics, AUTH, natsisthanasis@gmail.com]
  - Alkiviadis Bais^[Laboratory of Atmospheric Physics, AUTH]
abstract:
  "Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions."

@@

basic conceptions
